Case study validations of automatic bullet matching

### 2018-11-21 index.Rmd
JFS submission guidelines, keywords
todo

# to produce blinded version set to 1
blinded: 0

@@

keywords:
- 3 to 6 keywords
- that do not appear in the title

@@

\hh{
Cleanup TO-DO
\begin{itemize}
\item define false positives and false negatives once and stick to those definitions. We should avoid false positive and false negatives, because that only makes sense in a test setting, which we have not defined formally.
Let's use instead wrong identification and missed identification. 
\item error rates: we are using rates exchangeably with percentages. We need to fix that. I think percentages might be easier understood. XXX Should be fixed now
\end{itemize}
}

>>>>

# to produce blinded version set to 1
blinded: 1

@@

keywords:
- random forest
- 3d microscopy
- toolmark

@@

\hh{
Cleanup TO-DO
\begin{itemize}
\item \sout{define false positives and false negatives once and stick to those definitions. We should avoid false positive and false negatives, because that only makes sense in a test setting, which we have not defined formally.
Let's use instead wrong identification and missed identification. }
\item \sout{error rates: we are using rates exchangeably with percentages. We need to fix that. I think percentages might be easier understood. XXX Should be fixed now}
\end{itemize}
}
\svp{
Outstanding XXX items:
\begin{itemize}
\item thanks - scanning and hamby advice
\item comparison to FTEs in conclusion
\end{itemize}
}
